% !TEX program = xelatex
\documentclass{resume}
\usepackage{linespacing_fix}

\begin{document}
\pagenumbering{gobble}

\name{Garvey Fu}

\basicInfo{
  \email{loveforgeter@163.com} \textperiodcentered\ 
  \phone{(+86) 185-1669-3661}
}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{University of Electronic Science and Technology of China (UESTC)}, Chengdu, China}{2009 -- 2013}
\textit{B.S.} in Information Security

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Shanghai DZH Co.,Ltd.} Shanghai, China}{2013.7 -- 2015.7}
\role{C++ Development Engineer}{}
\begin{onehalfspacing}
    \textbf{DZH 365 Client}
    \begin{itemize}
        \item Implemented UI controls using C++.
        \item Implemented stock data presentation plugin.
        \item Implemented Stock-Plugin-Container for plugins management in client.
    \end{itemize}
\end{onehalfspacing}

\begin{onehalfspacing}
    \textbf{DZH Browser}
    \begin{itemize}
        \item Based on Firefox, customize UI and extend using plugins.
        \item Implemented login feature using javascript.
        \item Syncronize cookies for DZH sites using javascript.
        \item Integrated Stock-Plugin-Container using NPPluigin technique.
        \item Maintain MacOS version.
    \end{itemize}
\end{onehalfspacing}

\begin{onehalfspacing}
    \textbf{DZH Cloud Platform}
    \begin{itemize}
        \item Formula System cross platform support.
        \item Develop Formula System SDK using golang and cgo.
        \item Implemented formula import service, parse fomulas from file and save them to Redis storage using golang.
        \item Implemented stock index calculation service using golang, calculate common indices when stock data updated.
        \item Implemented Key-Elf service using golang, quick search stock data.
        \item Implemented grading fund calculation service, calculate when fund data updated.
    \end{itemize}
\end{onehalfspacing}

\datedsubsection{\textbf{Shanghai ECO Co.,Ltd.} Shanghai, China}{2015.7 -- Present}
AXENT IT Support Department, Startups
\role{iOS Development Engineer}{}
\begin{onehalfspacing}
    \textbf{AXENT iOS App}
    \begin{itemize}
        \item Design architecture.
        \item Implemented 360 degree product preview feature.
        \item Implemented product selection and presentation feature.
        \item Implemented offline feature.
        \item Multiple languages and regions support.
        \item Automate package and upload process using fastlane.
    \end{itemize}
\end{onehalfspacing}

\begin{onehalfspacing}
    \textbf{AXENT Console}
    \begin{itemize}
        \item Based on Akeneo PIM Community, for manage AXENT product data and customer relationships. Using Symfony Framework, Requirejs and BackboneJS.
        \item Develop AppBundle, provide product assets management feature.
        \item Develop CRMBundle, provide customers management feature.
        \item Implemented AXENT admin console frontend, including products management, dealers managment, users managment etc.
        \item Implemented AXENT dealer admin console frontend, including products management, price policies management, marketing feature etc.
        \item Refactor using React, Redux and Antd.
    \end{itemize}
\end{onehalfspacing}

\begin{onehalfspacing}
    \textbf{AXENT Wechat Weapp}
    \begin{itemize}
        \item Develop AXENT Wechat Weapp, same as iOS App.
    \end{itemize}
\end{onehalfspacing}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Swift == Objective-C > Javascript > Golang == C/C++ > PHP
  \item Platforms: MacOS, Windows
  \item Tools: Visual Studio Code, XCode
\end{itemize}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item GitHub: https://github.com/loveforgeter
  \item Languages: English - Fluent, Mandarin - Native speaker
\end{itemize}

\end{document}
